Prop off

### 2021-02-16 analysis/rev_prototyping/jackknife.Rmd
run som stuffs

>>>>

misc <- load_dataset("misc_abund_short")

misc_jacknifes <- jacknife_whole_dataset(misc)

write.csv(misc_jacknifes, here::here("analysis", "rev_prototyping", "jacknifed_datasets", "misc_jk.csv"), row.names = F)

bbs <- load_dataset("bbs")

bbs_jacknifes <- jacknife_whole_dataset(bbs)

write.csv(bbs_jacknifes, here::here("analysis", "rev_prototyping", "jacknifed_datasets", "bbs_jk.csv"), row.names = F)

gentry <- load_dataset("gentry")

gentry_jacknifes <- jacknife_whole_dataset(gentry)

write.csv(gentry_jacknifes, here::here("analysis", "rev_prototyping", "jacknifed_datasets", "gentry_jk.csv"), row.names = F)

### 2021-02-16 analysis/rev_prototyping/jackknife_mcdb_results.Rmd
run som stuffs

jk_di <- read.csv(here::here("analysis", "rev_prototyping", "mcdb_jk_di.csv"))

@@

wide_di <- left_join(jk_di, all_di) %>%
  group_by(site_source) %>%
  mutate(mean_skew_percentile_excl = mean(skew_percentile_excl),
         mean_simpson_percentile = mean(simpson_percentile),
         mean_nparts = mean(nparts)) %>%
  ungroup() %>%
  mutate(actual_sig_skew = skew_percentile_excl_actual > 95,
         actual_sig_even = simpson_percentile_actual < 5,
         mean_sig_skew = mean_skew_percentile_excl > 95,
         mean_sig_even = mean_simpson_percentile < 5) %>%
  mutate(skew_change = paste0("actual", actual_sig_skew, "_jk", mean_sig_skew),
         even_change = paste0("actual", actual_sig_even,"_jk", mean_sig_even))

@@

@@

ggplot(wide_di, aes(s0_actual, n0_actual, color = skew_change)) +
  geom_point()

@@

ggplot(wide_di, aes(nparts_actual, mean_nparts, color = skew_change)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  geom_line(aes(nparts_actual, nparts_actual), color = "black")

>>>>

jk_di <- read.csv(here::here("analysis", "rev_prototyping", "mcdb_di_jk.csv"))

@@

wide_di <- left_join(jk_di, all_di) %>%
  group_by(site_source) %>%
  mutate(mean_skew_percentile_excl = mean(skew_percentile_excl),
         mean_simpson_percentile = mean(simpson_percentile),
         mean_shannon_percentile = mean(shannon_percentile),
         mean_nparts = mean(nparts)) %>%
  ungroup() %>%
  mutate(actual_sig_skew = skew_percentile_excl_actual > 95,
         actual_sig_even = simpson_percentile_actual < 5,
         mean_sig_skew = mean_skew_percentile_excl > 95,
         mean_sig_even = mean_simpson_percentile < 5,
         actual_sig_shannon = shannon_percentile_actual < 5,
         mean_sig_shannon=  mean_shannon_percentile < 5) %>%
  mutate(skew_change = paste0("actual", actual_sig_skew, "_jk", mean_sig_skew),
         even_change = paste0("actual", actual_sig_even,"_jk", mean_sig_even),
         shannon_change = paste0("actual", actual_sig_shannon, "_jk", mean_sig_shannon))

@@

wide_di_small <- wide_di %>%
  select(site_source, mean_skew_percentile_excl, mean_simpson_percentile, s0, n0, mean_nparts, skew_change, even_change, actual_sig_skew, actual_sig_even, mean_sig_skew, mean_sig_even, mean_shannon_percentile, actual_sig_shannon, mean_sig_shannon, shannon_change) %>%
  filter(s0 > 2,
         s0 != n0,
         n0 != s0 + 1) %>%
  distinct()

ggplot(wide_di_small, aes(mean_skew_percentile_excl)) +
  geom_histogram()

ggplot(wide_di_small, aes(mean_simpson_percentile)) +
  geom_histogram()

ggplot(wide_di_small, aes(mean_shannon_percentile)) +
  geom_histogram()

mean(wide_di_small$actual_sig_skew)
mean(wide_di_small$mean_sig_skew)

mean(wide_di_small$actual_sig_shannon)
mean(wide_di_small$mean_sig_shannon)

mean(wide_di_small$actual_sig_even)
mean(wide_di_small$mean_sig_even)

wide_di_small %>%
  group_by(even_change) %>%
  tally()

@@

ggplot(wide_di, aes(s0_actual, n0_actual, color = skew_change)) +
  geom_point() +
  facet_wrap(vars(skew_change))

@@

ggplot(wide_di, aes(nparts_actual, mean_nparts, color = skew_change)) +
  geom_point(alpha = .5) +
  scale_x_log10() +
  scale_y_log10() +
  geom_line(aes(nparts_actual, nparts_actual), color = "black")

### 2021-02-16 analysis/rev_prototyping/nsingletons_prelim_results.Rmd
run som stuffs

all_di <- read.csv(here::here("miscabund_di.csv"))

all_di <- all_di %>%
  filter(s0 > 1,
         s0 != n0,
         n0 != s0 + 1)

>>>>

all_di <- read.csv(here::here("analysis", "rev_prototyping", "mcdb_di.csv"))

all_di <- all_di %>%
  filter(s0 > 1,
         s0 != n0,
         n0 != s0 + 1,
         !singletons)

sum(all_di$nsingeltons_median == all_di$nsingletons_95)

ggplot(filter(all_di, nsingletons_95 > nsingeltons_median), aes(nsingletons_percentile)) +
  geom_histogram()

ggplot(filter(all_di, nsingletons_95 > nsingeltons_median), aes(nsingletons_percentile_excl)) +
  geom_histogram()
